Article title

### 2017-06-28 paper-webserver.tex
FIX: grammar?

Previously, we developed Superphy \cite{whiteside2016superphy} a online platform, targeting \textit{E. coli}, which determines Shiga toxin subtypes, AMR genes through the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and statistical significance tests between subgroups in associated metadata. Here we present Spfy, a complete rewrite of Superphy integrating our Panseq package \cite{laing2010pan} for pan-genomic analyses of accessory regions, long-term storage of results in a graph database, and containerization of services using Docker, a modern approach found in many web servers and proposed to mitigate the complexities of bioinformatic pipelines \cite{di2015impact}. Furthermore, Spfy takes a modular approach to tool integration and distributes analyses over a task queue, allowing modules to run in parallel. All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

>>>>

Previously we developed Superphy \cite{whiteside2016superphy}, an online platform, targeting \textit{E. coli}, which determines Shiga toxin subtypes, AMR genes using the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and provides statistical significance tests between subgroups in associated metadata. Here we present Spfy, a complete rewrite of Superphy integrating our Panseq package \cite{laing2010pan} for pan-genomic analyses of accessory regions, long-term storage of results in a graph database, and containerization of services using Docker, a modern approach found in many web servers and proposed to mitigate the complexities of bioinformatic pipelines \cite{di2015impact}. Furthermore, Spfy takes a modular approach to tool integration and distributes analyses over task queues, thereby allowing modules to run in parallel. All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

Spfy enables processing of thousands of genome sequences using multiple modules. By using task queue workers, enabled by the Python-based Redis Queue library, performance can quickly scale to available infrastructure. As a bioinformatics tool, we ensured reliability of the platform by integrating the open-source Sentry toolkit for real-time exception tracking. The use of Docker-Compose for orchestrating containers ensures that the entire platform, webservers, databases, and task workers, can be easily replicated by other researchers. We present Spfy as a template for brining advances in web application development and deployment to online bioinformatics platforms.
